\documentclass[a4paper，12pt]{article}
\usepackage{styles/iplouccfg}
\usepackage{styles/zhfontcfg}

\title{Weekly Meeting Minutes} 
\author{Qiu Xinxin}
\date{September 13, 2014}

\begin{document}

\maketitle

\section{Meeting host, time and place}

\begin{itemize}
\item Meeting host: Qiu Xinxin
\item Meeting time: 2:00pm September 12, 2014 
\item Meeting place: Conference Room B201, South Building of College of Information Science and Engineering 
\end{itemize}

\section{Meeting reports}

\begin{enumerate}
\item The fresh graduate students (Zhao Haiwei, Dai Jialun and Wang Ruchen) made the report：每周汇报之新人篇 , Teacher Zheng and other fellow students raised and solved some questions. 
\item Zhu Yafei shared the contents of VALSE paper reading: Robust Matrix Factorization with Unknown Noise.
\item Sun Xiaoqing made a report which is about login shell and non-login shell. 
\end{enumerate}

\section {Things to note}

\begin{itemize}
\item Everyone should watch the VALSE videos weekly, and pay more attention to the videos that is relevant to your research field.
\item About the regular meeting content: every meeting should have two or three topics, which are terse, short but forceful.
\end{itemize}

\section {Tasks in the next week }

\begin{itemize}
\item Discuss and Decide the main topics,  and make reports for the SFD2014 in the Friday.
\item Prepare for the programming communication with Guo Dongsheng and Cui Luji.
\item The next meeting will be hosted by Dai Jialun.
\end{itemize}


\end{document}
