\documentclass[a4paper，12pt]{article}

\usepackage{zhfontcfg}

\title{Weekly Meeting Minutes} 
\author{Wei Tengda}
\date{October 11, 2014}

\begin{document}

\maketitle

\section{Meeting host, time and place}

\begin{itemize}
\item Meeting host: Wei Tengda
\item Meeting time: 9:30am October 11, 2014 
\item Meeting place: Conference Room B201, South Building of College of Information Science and Engineering 
\end{itemize}

\section{Meeting reports}

\begin{enumerate}
\item A report about primal-dual methods was made by Wei Tengda.
\item Zhu Yafei shared her understanding of the articles which she had read recently.
\item Zhao Haiwei made a report about background modeling which is an important part of object detection.
\end{enumerate}

\section {Things to note}

\begin{itemize}
\item To improve the efficiency, the weekly meeting will not last more than 3 hours. It is proper to be 2-3 hours. The host should control the time seriously.
\item We should take turns to listen to VALSE.
\item What you learn is your choice. The teacher focuses on research agenda. Freedom is ours.
\item When we read an article, we should think more about it. We should not only learn it but also understand the author's mind, including how he comes up the idea, what he solves, what he doesn't solve and so on.
\item When we receive a mail, we should read it, think about it and make changes.
\item Every minute counts. We don't have one minute to waste because we have nothing. The time often flies without our awareness.
\end{itemize}

\section {Tasks in the next week }

\begin{itemize}
\item The next meeting will be hosted by Wu Bin.
\end{itemize}


\end{document}
