\documentclass[a4paper，12pt]{article}

\usepackage{zhfontcfg}

\title{Weekly Meeting Minutes} 
\author{Wang Ruchen}
\date{September 26, 2014}

\begin{document}

\maketitle

\section{Meeting host, time and place}

\begin{itemize}
\item Meeting host: Wang Ruchen
\item Meeting time: 2:00pm September 26, 2014 
\item Meeting place: Conference Room B201, South Building of College of Information Science and Engineering 
\end{itemize}

\section{Meeting reports}

\begin{enumerate}
\item Wu Bin made a report about web introduction. 
\item Zhao Haiwei made a report about object detection.
\item Zhu Yafei shared her understanding of the article —— ``Salient Object Detection:A Survey''.
\item Qiu Xinxin made the evaluation of the article —— ``基于重调和方程的扩散去噪模型的研究''.
\end{enumerate}

\section {Things to note}

\begin{itemize}
\item The first year graduate students should take measures to improve the class efficiency.
\item In the learning process, we must be strict with ourselves. Set goals and take feasible measures. For example, if you want to get a scholarship, you should make a specific plan.
\item Thirst for knowledge is an indispensable part in scientific research. In the work, we have to use the brain thinking to improve work efficiency.
\item Students, who have the similar research direction, should strengthen exchanges with each other. Communication and cooperation can help us make progress together.
\item If you find some information which are useful to others, please tell them. Help others, and then you will get the help of others.
\item In the study of a new field, speak your mind, and don't be afraid of mistakes.
\end{itemize}

\section {Tasks in the next week }

\begin{itemize}
\item The next meeting will be hosted by Wei Tengda.
\end{itemize}


\end{document}
